{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-13 documents/background.tex
scan-converter

\begin{autem}

{\Large {This has \textbf{nothing to do} with 5G communications.}}\\

I am comfortable making such a definitive statement.

The power levels required to even begin to observe this inactivation effect in practice are so high that, if conditions are not specifically tailored for clinical use, extensive burns will result within seconds. Even in this case, the effect is to eviscerate the virus, not to aid its spread.

Moreover, these frequency bands have been in almost continuous use not long after Jagadish Chandra Bose 1894; the world has been bathed in high-power 10 GHz pulses at least since the commissioning of the first centimeter-wave weather radars in 1959.

Countless far more prosaic explanations exist in the modern world, such as air travel.

If you have any concerns regarding this statement, please contact me. I would be happy to discuss this.

\end{autem}

@@

@@

@@

>>>>

@@

zotero citation graph?

@@

Pakhomov \cite{Comparative} expose frog heart cells. No effects.

In fact, this specific question is briefly noted in a comment by Saviot \cite{Comment2004} on

We also would like to point out that these normal modes
are damped when the virus particle is embedded inside a
liquid...when the virus is inside water, for example, there is not much acoustic impedance mismatch at the surface. For this reason the normal modes will be broad and have short lifetimes. Therefore, the objective of killing viruses by sending out sound waves that resonate and destroy them is probably unworkable in such a configuration.

@@

Of course, this is using an extremely sensitive assay, not an aggregate inactivation
